GA-based Training-Free NAS Algorithm with Hybrid Score Function

### 2023-03-04 paper/main.tex
beautify the layout of main.tex

% introduction
    Neural architecture search (NAS) has recently drawn a big amount of 
    attention, since the ability to automatically design a "good" neural 
    architecture. By leveraging machine learning algorithms (Zoph \& Le,\ \cite{https://doi.org/10.48550/arxiv.1611.01578}), 
    NAS algorithms can explore a search space, which is comprised of 
    numerous potential architectures, to find out a good architectures 
    that outperform those designed by human experts. In recent years, 
    the use of NAS is widespread, from object detection (Sun et al.,\ \cite{https://doi.org/10.48550/arxiv.2111.13336}), 
    image recognition (Mellor et al.,\ \cite{https://doi.org/10.48550/arxiv.2006.04647}) 
    and speech recognition (Zheng et al.,\ \cite{https://doi.org/10.48550/arxiv.2011.05649}, 
    Mehrotra et al.,\ \cite{mehrotra2021nasbenchasr}) to 
    natural language processing(Jiang et al.,\ \cite{jiang-etal-2019-improved}, 
    Klyuchnikov et al.,\ \cite{https://doi.org/10.48550/arxiv.2006.07116}, 
    Wang et al.,\ \cite{https://doi.org/10.48550/arxiv.2005.14187}).

>>>>

% introduction
    Neural architecture search (NAS) has recently drawn a big amount of 
    attention, since the ability to automatically design a "good" neural 
    architecture. By leveraging machine learning algorithms (Zoph \& Le,
    \ \cite{https://doi.org/10.48550/arxiv.1611.01578}), NAS algorithms 
    can explore a search space, which is comprised of numerous potential 
    architectures, to find out a good architectures that outperform those 
    designed by human experts. In recent years, the use of NAS is widespread, 
    from object detection (Sun et al.,\ \cite{https://doi.org/10.48550/arxiv.2111.13336}), 
    image recognition (Mellor et al.,\ \cite{https://doi.org/10.48550/arxiv.2006.04647}) 
    and speech recognition (Zheng et al.,\ \cite{https://doi.org/10.48550/arxiv.2011.05649}, 
    Mehrotra et al.,\ \cite{mehrotra2021nasbenchasr}) to natural language 
    processing(Jiang et al.,\ \cite{jiang-etal-2019-improved}, 
    Klyuchnikov et al.,\ \cite{https://doi.org/10.48550/arxiv.2006.07116}, 
    Wang et al.,\ \cite{https://doi.org/10.48550/arxiv.2005.14187}).
